Toxic Code Snippets on Stack Overflow

### 2017-11-14 cloverflow-tse/cloverflow.tex
Added my own version of Giuseppe's bio.

\begin{IEEEbiography}{Giuseppe Bianco}
	Biography text here.
\end{IEEEbiography}
\vspace{-0.5cm}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{giuseppe.png}}]{Giuseppe Bianco}
receives his bachelor degree in Computer Science from University of Molise (Italy) under supervision of  Dr.~Rocco Oliveto. He was an Erasmus exchange student at CREST centre, University College London, UK, for three months and was supervised by Dr.~Jens Krinke.~He is now a project manager at Corsi.it.
\end{IEEEbiography}
\vspace{-0.5cm}
